Visual Exploration of Climate Data, Using Icon-Annotated Maps

### 2011-08-25 paper.tex
shaded map instead of outline
filling in paper

\documentclass{article}
\includepackage{graphicx}

@@

# Drawing trend lines on map
#   - How to
#   - Comparison to coloring slope
#   - Reference to Grinstein icon plots
#   - Alexander Gribov's work

# Interactive graphics
# Data processing

# Perhaps the GHCN data? Not gridded
# NOAA data, almost grid, but over ocean, so maps more tricky
# NARCAP from NCAR?
# Fill in with NASA data, to start, try to put new data for final version

@@

Need a colorful map

@@

>>>>

\documentclass{article}
\usepackage{graphicx}

@@

% Drawing trend lines on map
%   - How to
%   - Comparison to coloring slope
%   - Reference to Grinstein icon plots
% Pickett RM and Grinstein GG (1988). Iconographics 
% displays for visualizing multidimensional data. 
% In Proc. IEEE Conference on Systems, Man, and Cybernetics, pages 514-19.
% Note the later work on metaphoric data display, garbage work!
%   - Alexander Gribov's work http://rosuda.org/software/Gauguin/gauguin.html

% Interactive graphics
% Data processing

% Perhaps the GHCN data? Not gridded
% NOAA data, almost grid, but over ocean, so maps more tricky
% NARCAP from NCAR?
% Fill in with NASA data, to start, try to put new data for final version

\maketitle

@@

Need a colorful map, facetted by year \& month

\begin{figure*}[htp]
\includegraphics[width=6in]{images/nasa-colored-map.png}
\caption{Facetted map of de-seasonalized temperature.}
\end{figure*}

@@

\begin{figure*}[htp]
\centerline{\includegraphics[width=4in]{images/nasa-deseas-trend.pdf}}
\caption{Time series icon at each location, showing de-seasonalized trend.}
\end{figure*}
